Capstone Movielens Report

### 2025-05-10 reports/capstone-movielens-report.draft4.Rmd
Draft report development:  function `model.tune.param_range` (in progress).

::: {.noteblock data-latex=""}
Note that the function assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter. That is, it is assumed to have a single minimum in the domain of definition.
:::

>>>>

::: {.noteblock data-latex=""}
Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter. That is, it is assumed that the function has a single minimum on the given interval.
:::

### 2025-05-10 reports/capstone-movielens-report.draft4.tex
Draft report development:  function `model.tune.param_range` (in progress).

\begin{noteblock}
Note that the function assumes that the dependence of the \texttt{RMSE}
on the input parameter is a monotonically decreasing function until a
minimum is reached and monotonically increasing thereafter. That is, it
is assumed to have a single minimum in the domain of definition.

>>>>

\begin{noteblock}
Note that the algorithm assumes that the dependence of the \texttt{RMSE}
on the input parameter is a monotonically decreasing function until a
minimum is reached and monotonically increasing thereafter. That is, it
is assumed that the function has a single minimum on the given interval.
